Replication file for the paper: A multidimensional feasibility evaluation of low-carbon scenarios

### 2021-05-11 Paper_replication_files.Rmd
fixing mistake with the technical indicator
Commenting out data import

```{python pyam_world_data}
#You can import the 1.5C dataset either by using a python package pyam (and the link through reticulate) or by loading it (Release 2.0) from the scenario explorer and saving it in the input folder

import pyam

df =pyam.read_iiasa(
    'IXSE_SR15',
    model='*',
    variable=["AR5 climate diagnostics|Temperature|Global Mean|MAGICC6|MED",
  "Emissions|CO2",
  "GDP|PPP",
  "Population",
  "Investment|Energy Supply", 
  "Investment|Energy Supply|Electricity",
  "Investment|Energy Supply|Electricity|Solar",
  "Investment|Energy Supply|Electricity|Wind",
  "Investment|Energy Supply|Electricity|Nuclear",
  "Investment|Energy Supply|Electricity|Transmission and Distribution",
  "Investment|Energy Supply|Electricity|Biomass|w/ CCS",
  "Investment|Energy Supply|Electricity|Coal|w/ CCS",
  "Capacity|Electricity|Coal",
  "Secondary Energy|Electricity|Coal",
  "Capacity|Electricity|Gas",
  "Capacity|Electricity|Wind",
  "Capacity|Electricity|Solar",
  "Capacity|Electricity|Biomass",
  "Primary Energy|Biomass",
  "Primary Energy|Solar",
  "Secondary Energy|Electricity|Wind",
  "Secondary Energy|Electricity|Gas",
  "Primary Energy|Oil",
  "Price|Primary Energy|Oil",
  "Price|Carbon",
  "Price|Secondary Energy|Electricity",
  "Secondary Energy|Electricity",
  "Secondary Energy|Electricity|Oil",
  "Secondary Energy|Electricity|Nuclear",
  "Secondary Energy|Electricity|Wind",
  "Secondary Energy|Electricity|Solar",
  "Secondary Energy|Electricity|Hydro",
  "Secondary Energy|Electricity|Biomass",
  "Secondary Energy|Electricity|Biomass|w/ CCS",
  "Secondary Energy|Electricity|Coal|w/ CCS",
  "Secondary Energy|Electricity|Gas|w/ CCS",
  "Secondary Energy|Electricity|Oil|w/ CCS",
  "Final Energy|Transportation",
  "Final Energy|Transportation|Electricity",
  "Final Energy|Transportation|Liquids|Biomass",
  "Land Cover",
  "Land Cover|Forest",
  "Land Cover|Cropland",
  "Land Cover|Pasture",
  "Carbon Sequestration|Land Use",
  "Final Energy",
  "Final Energy|Residential and Commercial",
  "Final Energy|Industry",
  "Food Demand",
  "Food Demand|Livestock",
  "Final Energy|Industry|Electricity",
  "Final Energy|Residential and Commercial|Electricity",
  "Price|Agriculture|Livestock|Index",
  "Price|Agriculture|Corn|Index",
  "Emissions|NOx"],
   region='World'
)

df.to_csv('input/full.csv')

@@

```{python pyam_region_data}
#You can import the 1.5C dataset either by using a python package pyam (and the link through reticulate) or by loading an .csv file (Release 2.0) from the scenario explorer and saving it in the input folder

import pyam

df2 =pyam.read_iiasa(
    'IXSE_SR15',
    model='*',
    variable=[
  "Emissions|CO2",
  "GDP|PPP",
  "Population"]
)

df2.to_csv('input/region.csv')
```

@@

>>>>

```{python pyam_world_data, include=FALSE, MESSAGE=FALSE}
#You can import the 1.5C dataset either by using a python package pyam (and the link through reticulate) or by loading it (Release 2.0) from the scenario explorer and saving it in the input folder

#For this replication file the data was already prepared and is in the input folder

# import pyam
# 
# df =pyam.read_iiasa(
#     'IXSE_SR15',
#     model='*',
#     variable=["AR5 climate diagnostics|Temperature|Global Mean|MAGICC6|MED",
#   "Emissions|CO2",
#   "GDP|PPP",
#   "Population",
#   "Investment|Energy Supply",
#   "Investment|Energy Supply|Electricity",
#   "Investment|Energy Supply|Electricity|Solar",
#   "Investment|Energy Supply|Electricity|Wind",
#   "Investment|Energy Supply|Electricity|Nuclear",
#   "Investment|Energy Supply|Electricity|Transmission and Distribution",
#   "Investment|Energy Supply|Electricity|Biomass|w/ CCS",
#   "Investment|Energy Supply|Electricity|Coal|w/ CCS",
#   "Capacity|Electricity|Coal",
#   "Secondary Energy|Electricity|Coal",
#   "Capacity|Electricity|Gas",
#   "Capacity|Electricity|Wind",
#   "Capacity|Electricity|Solar",
#   "Capacity|Electricity|Biomass",
#   "Primary Energy|Biomass",
#   "Primary Energy|Solar",
#   "Secondary Energy|Electricity|Wind",
#   "Secondary Energy|Electricity|Gas",
#   "Primary Energy|Oil",
#   "Price|Primary Energy|Oil",
#   "Price|Carbon",
#   "Price|Secondary Energy|Electricity",
#   "Secondary Energy|Electricity",
#   "Secondary Energy|Electricity|Oil",
#   "Secondary Energy|Electricity|Nuclear",
#   "Secondary Energy|Electricity|Wind",
#   "Secondary Energy|Electricity|Solar",
#   "Secondary Energy|Electricity|Hydro",
#   "Secondary Energy|Electricity|Biomass",
#   "Secondary Energy|Electricity|Biomass|w/ CCS",
#   "Secondary Energy|Electricity|Coal|w/ CCS",
#   "Secondary Energy|Electricity|Gas|w/ CCS",
#   "Secondary Energy|Electricity|Oil|w/ CCS",
#   "Final Energy|Transportation",
#   "Final Energy|Transportation|Electricity",
#   "Final Energy|Transportation|Liquids|Biomass",
#   "Land Cover",
#   "Land Cover|Forest",
#   "Land Cover|Cropland",
#   "Land Cover|Pasture",
#   "Carbon Sequestration|Land Use",
#   "Final Energy",
#   "Final Energy|Residential and Commercial",
#   "Final Energy|Industry",
#   "Food Demand",
#   "Food Demand|Livestock",
#   "Final Energy|Industry|Electricity",
#   "Final Energy|Residential and Commercial|Electricity",
#   "Price|Agriculture|Livestock|Index",
#   "Price|Agriculture|Corn|Index",
#   "Emissions|NOx"],
#    region='World'
# )
# 
# df.to_csv('input/full.csv')

@@

```{python pyam_region_data, include=FALSE, MESSAGE=FALSE}
#You can import the 1.5C dataset either by using a python package pyam (and the link through reticulate) or by loading an .csv file (Release 2.0) from the scenario explorer and saving it in the input folder

#For this replication file the data was already prepare and is in the input folder

# import pyam
# 
# df2 =pyam.read_iiasa(
#     'IXSE_SR15',
#     model='*',
#     variable=[
#   "Emissions|CO2",
#   "GDP|PPP",
#   "Population"]
# )
# 
# df2.to_csv('input/region.csv')
```

@@

t<-c("concern_wind","concern_solar","concern_nuclear","concern_biomass","concern_biomass_ccs","concern_coal_ccs","concern_transport_e","concern_transport_bio")
